\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-03-20 paper/main.tex
.

We calculate the AUROC by computing true positive rate at various
false positive rate thresholds and using trapezoidal approximations to
estimate the area under the curve. We refer to this measure as
$MacroAUC$.

\todo[inline]{For RH: check this again later:}
In contrast we also calculate the $MicroAUC$ score. For given lists $D, P$ of drugs and proteins, respectively, and a set of known interactions $Int := \{(d_i, p_i) \}$, \textit{MicroAUC} is calculated as the average per entity (macro) \textit{AUROC} score. With respect to proteins, this can be formalized for given labels $l:D\times P \rightarrow \{0,1\}$ and predictions $y:D\times P \rightarrow [0,1]$  as 
\begin{equation*}
	MicroAUC_p := \underset{p\in P}{mean}\left(\left\{ \text{AUROC}(\{ (l(d_i, p), y(d_i,p))| d_i\in D\}) \right\}\right)
\end{equation*}

Drugs and proteins can be interchanged in this formulation, while we
refer to the different measures as protein-centric microAUC
($MicroAUC_p$) and a drug-centric microAUC
($MicroAUC_d$). Additionally, the $MicroAUC$ score may not be defined
as in some datasets some targets or drugs, respectively, do not have
any interactions, leading to an infeasible $TPR=0$ for all thresholds and an undefined
$AUROC$ score for that entity. For those entities we impute the $MicroAUC$ interpolating linearly, by using the accuracy for this subset.

>>>>

We calculate the AUROC by computing true positive rate at various
false positive rate thresholds and use trapezoidal approximations to
estimate the area under the curve. We refer to this measure as
$\textrm{MacroAUC}$.

\todo[inline]{For RH: check this again later:}
We also calculate the $\textrm{MicroAUC}$ score. For given lists $D$
and $P$ of drugs and proteins, respectively, and a set of known
interactions $Int := \{(d_i, p_i) \}$, \textit{MicroAUC} is calculated
as the average per entity (macro) \textit{AUROC} score. Specifically,
for protein-centric score, this can be formalized as: given labels
$l:D\times P \rightarrow \{0,1\}$ and predictions $y:D\times P
\rightarrow [0,1]$, we define
\begin{equation*}
  \textrm{MicroAUC}_p := \underset{p\in P}{mean}\left(\left\{
      \text{AUROC}(\{ (l(d_i, p), y(d_i,p))| d_i\in D\})
    \right\}\right)
\end{equation*}

Drugs and proteins can be interchanged in this formulation, and we
refer to the different measures as protein-centric microAUC
($MicroAUC_p$) and a drug-centric microAUC ($MicroAUC_d$). In some
cases, the $MicroAUC$ score may not be defined because in some
datasets some proteins or drugs have no interactions, leading to an
infeasible $TPR=0$ for all thresholds and an undefined $AUROC$ score
for that entity. For those entities, we impute the $MicroAUC$
interpolating linearly, by using the accuracy for this
subset\todo{Last sentence not clear, can you give the formula instead?}.
